---
title: "HW6"
output:   
  github_document
---

### Load packages and initial setup
```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)
library(mgcv)
library(modelr)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Question 1

## Question 2

Import data. Create variables `city_state`, `solved` indicator variable. 

```{r}
post <- read_csv("https://raw.github.com/washingtonpost/data-homicides/master/homicide-data.csv") %>%
  janitor::clean_names() %>%
  mutate(city_state = paste(city, state, sep =  ", "),
         solved = ifelse(disposition == "Closed by arrest", 1, 0),
         victim_age = as.numeric(recode(victim_age, "Unknown" = ""))) %>%
  filter((city_state != "Tulsa, AL" & city_state != "Dallas, TX" & city_state != "Phoenix, AZ" & city_state != "Kansas City, MO") & (victim_race == "White" | victim_race == "Black")) %>%
  select(city_state, everything())
```

Fit logistic regression model using `glm`. `solved` is the outcome and `victim_age`, `victim_sex`, and `victim_race` are predictors. 

Among homicides in Baltimore, MD

```{r}
fit <-
  post %>%
  filter(city_state == "Baltimore, MD") %>%
  glm(solved ~ victim_age + victim_sex + victim_race, family = binomial (link = "logit"), data = .)

fit %>%
  broom::tidy(conf.int = TRUE) %>%
  mutate(OR = exp(estimate), 
         OR_conf_low = exp(conf.low), 
         OR_conf_high = exp(conf.high)) %>%
  select(term, log_OR = estimate, OR, OR_conf_low, OR_conf_high) %>%
  knitr::kable(digits = 3)
```


Among all cities

```{r}
model_func <- function(x){
  glm(solved ~ victim_age + victim_sex + victim_race, family = binomial (link = "logit"), data = x) %>%
  broom::tidy(conf.int = TRUE) %>%
  mutate(OR = exp(estimate), 
         OR_conf_low = exp(conf.low), 
         OR_conf_high = exp(conf.high)) %>%
  select(term, log_OR = estimate, OR, OR_conf_low, OR_conf_high) %>%
  filter(term == "victim_sexMale")
}

all_nest <-
  post %>%
  nest(data = -city_state) %>%
  mutate(est = map(data, model_func)) %>%
  unnest(est)

```

Plot showing estimated ORs and CIs for each city, organizing cities according to estimated OR.

```{r}
all_nest %>%
  ggplot(aes(reorder(city_state, OR), OR)) +
  geom_errorbar(aes(min = OR_conf_low, max = OR_conf_high)) +
  geom_point(aes(color = city_state)) +
  labs(
    title = "Plot of Adjusted OR and CI of solved homicides comparing male to female victims",
    x = "City, State",
    y = "Adjusted OR"
  ) +
  theme(axis.text.x = element_text(angle = 90),
        legend.position = "none")
```

From the plot, on average, the adjusted ORs for most cities are below 1, suggesting that male victims have a smaller odds of having a solved homicide case compared to females. Additionally, we see the confidence interval for many cities contains the null value of 1, indicating results are not significant. 

## Question 3

```{r}
weight <-
  read.csv("data/birthweight.csv") %>%
  mutate(id = row_number(),
         babysex = as.factor(babysex),
         frace = as.factor(frace),
         mrace = as.factor(mrace),
         malform = as.factor(malform))
```

```{r}
str(weight)
sapply(weight, function(x) sum(is.na(x)))
```

No missing values in dataset, `id` variable created, `babysex`, `frace`, `mrace`, and `malform` converted to factor variables.

```{r}
weight %>%
  ggplot(aes(x = bwt)) + 
  geom_histogram(binwidth = 30) +
  labs(
    title = "Distribution of Birthweight",
    x = "Birthweight (g)",
    y = "Count"
  )
```

`bwt` is relatively normally distributed.

